On the minimum leaf conductance

### 2017-08-01 manuscript.Rmd
Use new database; Rmd with all figures; some figures redone with new grouping

>>>>

Mackova (Environmental and Experimental Botany Volume 86, February 2013, Pages 70-75): adding ABA to Lepidium sativum increased the chain length of cuticular waxes (but not total amounts). Other work has shown that the length of the chain decreases cuticular transpiration (they cite Hauke and Schreiber, 1998 Ontogenetic and seasonal development of wax composition and cuticular transpiration of ivy (Hedera helix L.) sun and shade leaves)

@rosasanderson2014, (2013, thesis), lower gmin in drought-stressed peanut
